Verifying Demonstrations

### 2017-08-27 properties.tex
Edits properties, shortens text, improves temporal with fig

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{frame}
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous protests.
  \item Alice must provide data which can be used for the desired verification.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}
\end{frame}
Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the location that the photo is portraying, however, 
this might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
Furthermore, how can Alice protect the privacy of those in the photos?

@@

\mode<presentation>{%
\begin{frame}
\begin{idea}[Temporal eligibility]
  \begin{itemize}
    \item There is a mechanism that provides the properties of a poset: a 
      blockchain.

    \item There are also other structures, e.g.\ a directed 
      graph~\cite{BlockchainFreeCryptocurrencies}.
  \end{itemize}
\end{idea}
\end{frame}
}

\begin{frame}
\begin{figure}
  \centering
  \input{fig-tposet.tex}
  \mode<article>{%
    \caption{%
      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
      are incomparable.
    }\label{PosetGraph}
  }
\end{figure}

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included (duh!).
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<2>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

>>>>

Alice is an activist who organizes a demonstration for some cause.
Her main goal after the protest is to provide verifiable data.
There are several problems:
\begin{itemize}
  \item Alice must prove that the data is related to the event, that it is not 
    reused data from previous protests.
  \item Alice must provide data which can be used for the desired verification.
  \item Alice must also consider the privacy of the participating individuals.
\end{itemize}

\begin{frame}<presentation>
  \begin{itemize}
    \item Alice must prove that the data is related to the event.
    \item Alice must provide data with verifiable properties.
    \item Alice must consider the privacy of the participants.
  \end{itemize}
\end{frame}

Since many of the current techniques are based on photos, we will give an 
example of Alice's problems in that setting.
How can she ensure that photos from a demonstration are authentic?
We can probably recognize the location that the photo is portraying, however, 
this might just as well be a reconstruction or entirely computer generated.
We cannot trust the meta-data of the photo, such as time-stamps of the file, 
because these can easily be manipulated.
So the only thing we can say for sure is that the photo was taken at the latest 
at the time of publication.
Now, if we cannot trust these photos, how can we determine the number of 
participants of a demonstration?
Furthermore, how can Alice protect the privacy of those in the photos?

@@

\begin{frame}
\begin{figure}
  \centering
  \input{fig/tposet.tex}
  \mode<article>{%
    \caption{%
      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
      are incomparable.
    }\label{PosetGraph}
  }
\end{figure}

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Temporal eligibility]
      \begin{itemize}
        \item We need a partially ordered set (poset).
        \item There is a mechanism that provides this property: a blockchain.
        \item There are also other structures, e.g.\ a directed 
          graph~\cite{BlockchainFreeCryptocurrencies}.
      \end{itemize}
    \end{idea}
  }
  \only<2>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included (duh!).
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<3>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}
